---
title: "Análise do Brasileirão"
author: "Lívia Cavalcanti"
date: "4 de junho de 2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
theme_set(theme_bw())

library(broom)

knitr::opts_chunk$set(tidy = FALSE,
                      fig.width = 6,
                      fig.height = 5)
```

```{r}
dados_gols <- read_csv2(("campeonato-brasileiro-full.csv"))
```

```{r}
head(dados_gols)
```

```{r}
qua_dom_jogos <- dados_gols %>% 
                    filter(Dia == "Domingo" | Dia == "Quarta-feira")
```

theta_diferenca = function(d, i){
    sonos = d %>% 
        slice(i) %>% 
        group_by(turma) %>% 
        summarise(sono = mean(sono_semana)) 
    
    cdd = sonos %>% filter(turma == "cdd") %>% pull(sono)
    fpcc = sonos %>% filter(turma == "fpcc") %>% pull(sono)
    
    cdd - fpcc
}

```{r}
theta_diferenca_gols <- function(df, i) {
  gols_df = df %>%
          slice(i) %>%
            group_by(Dia) %>%
              summarise(gols_media = mean(gols))
  
  dom = gols_df %>% filter(Dia == "Domingo") %>% pull(gols_media)
  qua = gols_df %>% filter(Dia != "Domingo") %>% pull(gols_media)
  
  dom - qua
}
```


theta_embaralhado = function(d){
    sonos = d %>% 
        mutate(turma_embaralhada = sample(turma, n())) %>% 
        group_by(turma_embaralhada) %>% 
        summarise(sono = mean(sono_fds)) 
    
    cdd = sonos %>% filter(turma_embaralhada == "cdd") %>% pull(sono)
    fpcc = sonos %>% filter(turma_embaralhada == "fpcc") %>% pull(sono)
    
    cdd - fpcc
}

theta_embaralhado(dados)

```{r}
theta_hipotese_gols <- function(df) {
  gols_df = df %>%
            mutate(embaralhados_jogos = sample(Dia, n())) %>%
              group_by(embaralhados_jogos) %>%
                summarise(gols_media = mean(gols))
  
  dom = gols_df %>% filter(embaralhados_jogos == "Domingo") %>% pull(gols_media)
  qua = gols_df %>% filter(embaralhados_jogos != "Domingo") %>% pull(gols_media)
  
  dom - qua
}


```


```{r}
diffs_gols = replicate(5000, {theta_hipotese_gols(qua_dom_jogos)})




tibble(diferenca = diffs_gols) %>% 
  ggplot(aes(x = diferenca)) + 
    geom_density(fill = "white", color = "darkgreen") +
  geom_vline(xintercept = theta_diferenca_gols(qua_dom_jogos, 1:NROW(qua_dom_jogos)),
             color = "orange") +
    geom_vline(xintercept = - theta_diferenca_gols(qua_dom_jogos, 1:NROW(qua_dom_jogos)),
             color = "orange")
```

